---
title: "The clock is ticking: temporally prioritising eradications on islands"
output: html_document
---
## Parametric distribution evaluation

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Distributions, include= FALSE}
source("code/R/analysis/00-initialization.R")
source("code/R/analysis/01-survDist.R")
```

Non-parametric (Kaplan-Meier) survival curve of the survival data used in this study.
```{r km curve, echo = FALSE}
  suppressMessages(attach(surv_data)) %>%
    na.omit(surv_data)
  surv_data <- mutate(surv_data, all = Event != 0)
  surv.obj <- Surv(surv_data$Erad_Time, surv_data$all)
  fit_km <- survfit(surv.obj ~ 1,
                    data = surv_data)
    survminer::ggsurvplot(fit_km, 
                           risk.table = FALSE, 
                           xlab = "Time (yrs)", 
                           censor = T, palette = "black", 
                           conf.int = FALSE, 
                           legend = "none", 
                           linetype = 1)
```

The kaplan-meier (KM) non-parametric curve for our survival data was fitted with nine relevant right-skewed parametric distributions in order to determine which curve best described New Zealand's terrestrial vertebrate eradication history.

```{r Distribution eval, echo= FALSE}
#fit KM curve to parametric distributions
fit_survDistr(surv_data, 
              surv_parameters$base_distr,
              surv_parameters$custom_distr,
              surv_parameters$t0,
              surv_parameters$t1,
              surv_parameters$t2)
```

The best fitting distributions (based on maximum log likelihoods) include the inverse gaussian, inverse gamma and burr.
